Extreme Value Chapter

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
I like the boxplots

```{r fig.width=10, fig.height=3}
thetas %>% 
  ggplot(., aes(x = thresh_tests, y = theta)) +
  geom_point(size = 4, shape = 18, color = theta_color) +
  labs(x = "Long-distance level", y = "Theta") +
  theme_bw() -> a

@@

```{r fig.width=12}
nreps_mles_df %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_point() +
  labs(x = "Long-distance level", y = "Estimated thetas") +
  theme_bw()

@@

>>>>

```{r fig.width=6, fig.height=2}
thetas %>% 
  ggplot(., aes(x = thresh_tests, y = theta)) +
  geom_point(size = 4, shape = 18, color = theta_color) +
  labs(x = "Long-distance level", y = "Theta") +
  theme_bw() -> a

@@

```{r fig.width=6, fig.height=4}
nreps_mles_df %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_point(alpha = 0.8, size = 3, color = "grey27") +
  labs(x = "Long-distance level", y = "Estimated thetas", title = "Simple Lomax") +
  scale_x_continuous(breaks = thresh_tests) +
  theme_bw() -> a

nreps_mles_df %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_point(alpha = 0.8, size = 3, color = "grey27") +
  labs(x = "Long-distance level", y = "Estimated thetas", title = "GLM Lomax") +
  scale_x_continuous(breaks = thresh_tests) +
  theme_bw() -> b

plot_grid(a, b, nrow = 2)

@@

Since there are so many points, we can see them a little more scattered with jitter:

```{r fig.width=6, fig.height=4}
nreps_mles_df %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_jitter(alpha = 0.8, size = 3, color = "grey27") +
  labs(x = "Long-distance level", y = "Estimated thetas", title = "Simple Lomax") +
  scale_x_continuous(breaks = thresh_tests) +
  theme_bw() -> a

nreps_mles_df %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_jitter(alpha = 0.8, size = 3, color = "grey27") +
  labs(x = "Long-distance level", y = "Estimated thetas", title = "GLM Lomax") +
  scale_x_continuous(breaks = thresh_tests) +
  theme_bw() -> b

plot_grid(a, b, nrow = 2)
```

But we are seeing aggregated data, and we tested at different sample sizes:

```{r fig.width=8, fig.height=4}
nreps_mles_df %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_jitter(alpha = 0.8, size = 3, aes(color = factor(samp_n_tests))) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Long-distance level", y = "Estimated thetas", title = "Simple Lomax") +
  scale_x_continuous(breaks = thresh_tests) +
  theme_bw() +
  theme(legend.position = "none") -> a

nreps_mles_df %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_jitter(alpha = 0.8, size = 3, aes(color = factor(samp_n_tests))) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Long-distance level", y = "Estimated thetas", title = "GLM Lomax") +
  scale_x_continuous(breaks = thresh_tests) +
  theme_bw() +
  theme(legend.position = "right") + 
  guides(color = guide_legend(title = "Sample Size")) -> b

ableg <- get_legend(b)

abplot <- plot_grid(a, b + theme(legend.position = "none"), nrow = 2)

plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.3))

Can I see this as boxplots or something else? To see the differences in sample size more clearly.

```{r fig.width=8, fig.height=4}
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat, fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Long-distance level", y = "Theta hat", title = "Simple Lomax") +
  theme_bw() +
  theme(legend.position = "none") -> a

nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2, fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Long-distance level", y = "Theta hat", title = "GLM Lomax") +
  theme_bw() +
  theme(legend.position = "right") -> b

ableg <- get_legend(b)

abplot <- plot_grid(a, b + theme(legend.position = "none"), nrow = 2)

plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.3))
